Response to reviewers

### 2024-11-29 Analysis/04_Summarise_results.Rmd
added 500 and 1000 elements

@@

@@

## Extracting all the results but not centred (still scaled)
raw_results_2d <- extract.table(all_results_2d, scale.method = "between", centre = FALSE)
raw_results_3d <- extract.table(all_results_3d, scale.method = "between", centre = FALSE)
raw_results_4d <- extract.table(all_results_4d, scale.method = "between", centre = FALSE)
raw_results_5d <- extract.table(all_results_5d, scale.method = "between", centre = FALSE)
raw_results_8d <- extract.table(all_results_8d, scale.method = "between", centre = FALSE)
raw_results_emp<- extract.table(empirical_results, scale.method = "between", centre = FALSE)
```

@@

## Making the fancy tables for the models
model_table_2d  <- fancy.table(model_fits_2d, columns = list(c(3,4), 5))
model_table_3d  <- fancy.table(model_fits_3d, columns = list(c(3,4), 5))
model_table_4d  <- fancy.table(model_fits_4d, columns = list(c(3,4), 5))
model_table_5d  <- fancy.table(model_fits_5d, columns = list(c(3,4), 5))
model_table_8d  <- fancy.table(model_fits_8d, columns = list(c(3,4), 5))
model_table_emp <- fancy.table(model_fits_emp, columns = list(c(3,4), 5))
## For the differences
columns_diff_ses <- list(c(1,3), 4)
columns_diff_ses <- c(columns_diff_ses,
                      lapply(columns_diff_ses, `+`, 4),
                      lapply(columns_diff_ses, `+`, 8),
                      lapply(columns_diff_ses, `+`, 12))
null_table_2d   <- fancy.table(null_differences_2d, columns = columns_diff_ses, digits = 2)
null_table_3d   <- fancy.table(null_differences_3d, columns = columns_diff_ses, digits = 2)
null_table_4d   <- fancy.table(null_differences_4d, columns = columns_diff_ses, digits = 2)
null_table_5d   <- fancy.table(null_differences_5d, columns = columns_diff_ses, digits = 2)
null_table_8d   <- fancy.table(null_differences_8d, columns = columns_diff_ses, digits = 2)
null_table_emp  <- fancy.table(null_differences_emp, columns = list(c(1,3), 4, c(1,3)+4, 4+4), digits = 2)
```

@@

>>>>

all_results_2d500 <- read.results("2d500")
all_results_4d500 <- read.results("4d500")
all_results_2d1000 <- read.results("2d1000")
all_results_4d1000 <- read.results("4d1000")

@@

all_results_2d500 <- lapply(all_results_2d500, sort.metrics, order = new_order)
all_results_4d500 <- lapply(all_results_4d500, sort.metrics, order = new_order)
all_results_2d1000 <- lapply(all_results_2d1000, sort.metrics, order = new_order)
all_results_4d1000 <- lapply(all_results_4d1000, sort.metrics, order = new_order)

@@

scaled_results_2d500 <- extract.table(all_results_2d500, scale.method = "between")
scaled_results_4d500 <- extract.table(all_results_4d500, scale.method = "between")
scaled_results_2d1000 <- extract.table(all_results_2d1000, scale.method = "between")
scaled_results_4d1000 <- extract.table(all_results_4d1000, scale.method = "between")

## Extracting all the results but not centred (still scaled)
raw_results_2d <- extract.table(all_results_2d, scale.method = "between", centre = FALSE)
raw_results_3d <- extract.table(all_results_3d, scale.method = "between", centre = FALSE)
raw_results_4d <- extract.table(all_results_4d, scale.method = "between", centre = FALSE)
raw_results_5d <- extract.table(all_results_5d, scale.method = "between", centre = FALSE)
raw_results_8d <- extract.table(all_results_8d, scale.method = "between", centre = FALSE)
raw_results_emp<- extract.table(empirical_results, scale.method = "between", centre = FALSE)

raw_results_2d500 <- extract.table(all_results_2d500, scale.method = "between", centre = FALSE)
raw_results_4d500 <- extract.table(all_results_4d500, scale.method = "between", centre = FALSE)
raw_results_2d1000 <- extract.table(all_results_2d1000, scale.method = "between", centre = FALSE)
raw_results_4d1000 <- extract.table(all_results_4d1000, scale.method = "between", centre = FALSE)

@@

## Making the fancy tables for the models
model_table_2d  <- fancy.table(model_fits_2d, columns = list(c(3,4), 5))
model_table_3d  <- fancy.table(model_fits_3d, columns = list(c(3,4), 5))
model_table_4d  <- fancy.table(model_fits_4d, columns = list(c(3,4), 5))
model_table_5d  <- fancy.table(model_fits_5d, columns = list(c(3,4), 5))
model_table_8d  <- fancy.table(model_fits_8d, columns = list(c(3,4), 5))
model_table_emp <- fancy.table(model_fits_emp, columns = list(c(3,4), 5))
## For the differences
columns_diff_ses <- list(c(1,3), 4)
columns_diff_ses <- c(columns_diff_ses,
                      lapply(columns_diff_ses, `+`, 4),
                      lapply(columns_diff_ses, `+`, 8),
                      lapply(columns_diff_ses, `+`, 12))
null_table_2d   <- fancy.table(null_differences_2d, columns = columns_diff_ses, digits = 2)
null_table_3d   <- fancy.table(null_differences_3d, columns = columns_diff_ses, digits = 2)
null_table_4d   <- fancy.table(null_differences_4d, columns = columns_diff_ses, digits = 2)
null_table_5d   <- fancy.table(null_differences_5d, columns = columns_diff_ses, digits = 2)
null_table_8d   <- fancy.table(null_differences_8d, columns = columns_diff_ses, digits = 2)
null_table_emp  <- fancy.table(null_differences_emp, columns = list(c(1,3), 4, c(1,3)+4, 4+4), digits = 2)

model_fits_2d500  <- lapply(scaled_results_2d500, fit.model.rm)
null_differences_2d500  <- lapply(all_results_2d500, paired.tests)
model_table_2d500  <- fancy.table(model_fits_2d500, columns = list(c(3,4), 5))
null_table_2d500   <- fancy.table(null_differences_2d500, columns = columns_diff_ses, digits = 2)
model_fits_4d500  <- lapply(scaled_results_4d500, fit.model.rm)
null_differences_4d500  <- lapply(all_results_4d500, paired.tests)
model_table_4d500  <- fancy.table(model_fits_4d500, columns = list(c(3,4), 5))
null_table_4d500   <- fancy.table(null_differences_4d500, columns = columns_diff_ses, digits = 2)

model_fits_2d1000  <- lapply(scaled_results_2d1000, fit.model.rm)
null_differences_2d1000  <- lapply(all_results_2d1000, paired.tests)
model_table_2d1000  <- fancy.table(model_fits_2d1000, columns = list(c(3,4), 5))
null_table_2d1000   <- fancy.table(null_differences_2d1000, columns = columns_diff_ses, digits = 2)
model_fits_4d1000  <- lapply(scaled_results_4d1000, fit.model.rm)
null_differences_4d1000  <- lapply(all_results_4d1000, paired.tests)
model_table_4d1000  <- fancy.table(model_fits_4d1000, columns = list(c(3,4), 5))
null_table_4d1000   <- fancy.table(null_differences_4d1000, columns = columns_diff_ses, digits = 2)

@@

```{r}
## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_2d500.pdf", height = 9, width = 9)
fancy.plot(scaled_results_2d500, col = col_vector, lm = model_fits_2d500, null = null_differences_2d500, metric.names = fancy_names, pch = rep(19,4))
dev.off()

pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_4d500.pdf", height = 9, width = 9)
fancy.plot(scaled_results_4d500, col = col_vector, lm = model_fits_4d500, null = null_differences_4d500, metric.names = fancy_names, pch = rep(19,4))
dev.off()

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_2d1000.pdf", height = 9, width = 9)
fancy.plot(scaled_results_2d1000, col = col_vector, lm = model_fits_2d1000, null = null_differences_2d1000, metric.names = fancy_names, pch = rep(19,4))
dev.off()

pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_4d1000.pdf", height = 9, width = 9)
fancy.plot(scaled_results_4d1000, col = col_vector, lm = model_fits_4d1000, null = null_differences_4d1000, metric.names = fancy_names, pch = rep(19,4))
dev.off()
```

### 2024-11-29 Manuscript/supplementaries.tex
added 500 and 1000 elements

>>>>

\begin{figure}[!htbp]
\centering
   \includegraphics[width=0.8\textwidth]{Figures/results_per_metric_per_stressor_2d500.pdf}
\caption{\scriptsize{\textbf{Simulation results for 2 dimensions and 500 observations (instead of 200):} the y axes represent the different metrics tested (sorted by categories).
The different columns represent the different stressors. The x-axes represent the metric values centred on the random changes and scaled by the maximum value for each metric between the four stressors.
Negative and positive values signify that the metric score for the stressor of interest is lower/higher than the one from the random stressor.
The dots represent the median metric value, the full line their 50\% confidence interval (CI) and the dashed line their 95\% CI.
The colours are here to visually separate the metrics by categories (blue = regularity, yellow = divergence, green = richness); the colour gradient within each row corresponds to a removal of respectively 80\%, 60\%, 40\% and 20\% of the data (from top to bottom).
The grey line plots represent distributions of metric scores not clearly distinguishable from the random metric scores (paired t-test p value $> 0.05$).
Grey lines in the background across the distributions of different removal amounts represent the fitted linear model centred and scaled metric score $\sim$ amount of data removed and the value displayed is the adjusted $R^2$ from each of these models.
Dashed thin grey lines represent non-significant models (p value of slope or/and intercept $> 0.05$).
\textbf{NOTE: for the \texttt{TPD} metrics, the metric is calculated using the 4 first dimensions only.}
}}
\label{Fig:simulation_results_2d500}
\end{figure}
\bigskip

\begin{figure}[!htbp]
\centering
   \includegraphics[width=0.8\textwidth]{Figures/results_per_metric_per_stressor_2d1000.pdf}
\caption{\scriptsize{\textbf{Simulation results for 2 dimensions and 1000 observations (instead of 200):} the y axes represent the different metrics tested (sorted by categories).
The different columns represent the different stressors. The x-axes represent the metric values centred on the random changes and scaled by the maximum value for each metric between the four stressors.
Negative and positive values signify that the metric score for the stressor of interest is lower/higher than the one from the random stressor.
The dots represent the median metric value, the full line their 50\% confidence interval (CI) and the dashed line their 95\% CI.
The colours are here to visually separate the metrics by categories (blue = regularity, yellow = divergence, green = richness); the colour gradient within each row corresponds to a removal of respectively 80\%, 60\%, 40\% and 20\% of the data (from top to bottom).
The grey line plots represent distributions of metric scores not clearly distinguishable from the random metric scores (paired t-test p value $> 0.05$).
Grey lines in the background across the distributions of different removal amounts represent the fitted linear model centred and scaled metric score $\sim$ amount of data removed and the value displayed is the adjusted $R^2$ from each of these models.
Dashed thin grey lines represent non-significant models (p value of slope or/and intercept $> 0.05$).
\textbf{NOTE: for the \texttt{TPD} metrics, the metric is calculated using the 4 first dimensions only.}
}}
\label{Fig:simulation_results_2d1000}
\end{figure}
\bigskip

\begin{figure}[!htbp]
\centering
   \includegraphics[width=0.8\textwidth]{Figures/results_per_metric_per_stressor_4d500.pdf}
\caption{\scriptsize{\textbf{Simulation results for 4 dimensions and 500 observations (instead of 200):} the y axes represent the different metrics tested (sorted by categories).
The different columns represent the different stressors. The x-axes represent the metric values centred on the random changes and scaled by the maximum value for each metric between the four stressors.
Negative and positive values signify that the metric score for the stressor of interest is lower/higher than the one from the random stressor.
The dots represent the median metric value, the full line their 50\% confidence interval (CI) and the dashed line their 95\% CI.
The colours are here to visually separate the metrics by categories (blue = regularity, yellow = divergence, green = richness); the colour gradient within each row corresponds to a removal of respectively 80\%, 60\%, 40\% and 20\% of the data (from top to bottom).
The grey line plots represent distributions of metric scores not clearly distinguishable from the random metric scores (paired t-test p value $> 0.05$).
Grey lines in the background across the distributions of different removal amounts represent the fitted linear model centred and scaled metric score $\sim$ amount of data removed and the value displayed is the adjusted $R^2$ from each of these models.
Dashed thin grey lines represent non-significant models (p value of slope or/and intercept $> 0.05$).
\textbf{NOTE: for the \texttt{TPD} metrics, the metric is calculated using the 4 first dimensions only.}
}}
\label{Fig:simulation_results_4d500}
\end{figure}
\bigskip

\begin{figure}[!htbp]
\centering
   \includegraphics[width=0.8\textwidth]{Figures/results_per_metric_per_stressor_4d1000.pdf}
\caption{\scriptsize{\textbf{Simulation results for 2 dimensions and 1000 observations (instead of 200):} the y axes represent the different metrics tested (sorted by categories).
The different columns represent the different stressors. The x-axes represent the metric values centred on the random changes and scaled by the maximum value for each metric between the four stressors.
Negative and positive values signify that the metric score for the stressor of interest is lower/higher than the one from the random stressor.
The dots represent the median metric value, the full line their 50\% confidence interval (CI) and the dashed line their 95\% CI.
The colours are here to visually separate the metrics by categories (blue = regularity, yellow = divergence, green = richness); the colour gradient within each row corresponds to a removal of respectively 80\%, 60\%, 40\% and 20\% of the data (from top to bottom).
The grey line plots represent distributions of metric scores not clearly distinguishable from the random metric scores (paired t-test p value $> 0.05$).
Grey lines in the background across the distributions of different removal amounts represent the fitted linear model centred and scaled metric score $\sim$ amount of data removed and the value displayed is the adjusted $R^2$ from each of these models.
Dashed thin grey lines represent non-significant models (p value of slope or/and intercept $> 0.05$).
\textbf{NOTE: for the \texttt{TPD} metrics, the metric is calculated using the 4 first dimensions only.}
}}
\label{Fig:simulation_results_4d1000}
\end{figure}
\bigskip

\subsection{Raw results}
